Impact of the 2016 Presidential Election on Urban Mobility: Who is Affected the Most?

### 2019-11-25 manuscript.Rmd
finished geoid join to uber travel times

```{r setup, include=FALSE}
library(tidyverse)
library(sf)
library(rgdal)

@@

head(travel_times)
```

```{r}
#Attempting to add roads in this code chunk

library(spdep)
library(sf)
roads<-st_read("dc_roads")
#row.names(roads) <- as.character(roads$FIPSNO)
#plot(st_geometry(roads), axes=TRUE)

#tigris package - contains roads for DC
options(tigris_class="sf")
#primary_secondary_roads includes interstates and other highways in DC
dc <- tigris::primary_secondary_roads(state="DC")
dc
plot(dc)
```

@@

```{r join_sf}
DC_census <- st_read("data/washington_DC_censustracts.json") %>%
	select("id" = MOVEMENT_ID, geometry) %>%
	mutate(id = factor(id, levels = levels(travel_times$dest_id)))

DC_census

travel_time_sf <- left_join(x = travel_times, y = DC_census, by = c("dest_id" = "id")) %>%
	st_as_sf() %>%
	st_transform(crs = 102285)

st_centroid(x = travel_time_sf)
```

```{r map}
travel_time_sf %>%
	ggplot() +
	geom_sf(mapping = aes(fill = mean_travel_time)) +
	theme_map +
	scale_fill_viridis_c(direction = -1)
```

```{r}
travel_time_sf %>% filter(year == 2017, month == 1, week == 3)%>%
	ggplot() +
	geom_sf(mapping = aes(fill = mean_travel_time)) +
	theme_map +
	scale_fill_viridis_c(direction = -1)

travel_time_sf %>% filter(year == 2017, month == 1, week == 4)%>%
	ggplot() +
	geom_sf(mapping = aes(fill = mean_travel_time)) +
	theme_map +
	scale_fill_viridis_c(direction = -1)
```

>>>>

```{r setup, include=FALSE}
library(tidyverse)
library(sf)
library(rgdal)
library(tigris)
library(spdep)

#tigris package - contains roads for DC
options(tigris_class="sf")

@@

#primary_secondary_roads includes interstates and other highways in DC
dc_roads <- primary_secondary_roads(state="DC") %>%
	st_transform(crs = 102285)
```

@@

```{r join_sf}
dc_census <- st_read("data/uber_dc_tracts.json") %>%
	select("id" = MOVEMENT_ID, geometry) %>%
	mutate(id = factor(id, levels = levels(travel_times$dest_id)))

travel_time_sf <- left_join(x = travel_times, y = dc_census, by = c("dest_id" = "id")) %>%
	st_as_sf() %>%
	st_transform(crs = 102285)
```

```{r map}
travel_time_sf %>% filter(year == 2017, month == 1, week == 3) %>%
	ggplot() +
	geom_sf(mapping = aes(fill = mean_travel_time)) +
	theme_map +
	scale_fill_viridis_c(direction = -1)

travel_time_sf %>% filter(year == 2017, month == 1, week == 4)%>%
	ggplot() +
	geom_sf(mapping = aes(fill = mean_travel_time)) +
	geom_sf(data = dc_roads) +
	theme_map +
	scale_fill_viridis_c(direction = -1)
```
